[![Build Status](https://travis-ci.org/JohnCoene/tippy.svg?branch=master)](https://travis-ci.org/JohnCoene/tippy) [![CRAN status](https://www.r-pkg.org/badges/version/tippy)](https://cran.r-project.org/package=tippy) [![](https://cranlogs.r-pkg.org/badges/tippy)](https://cran.r-project.org/package=tippy)

```{r, include=FALSE}
library(tippy)
library(htmltools)
```

```{r, echo=FALSE}
div(
  class = "row",
  div(
    class = "col-md-3",
    img(
      src = "logo.png",
      class = "responsive-img img-responsive"
    )
  ),
  div(
    class = "col-md-9",
    h1(
      tippy(
        "Tippy",
        "Tooltips!!!",
        size = "large"
      )
    ),
    br(),
    p(
      "A",
      tippy(
        "small package",
        "Just 4 functions!"
      ),
      "to include tooltips in Shiny apps and",
      tippy(
        "R Markdown documents",
        "Just like this one"
      )
    )
  )
)
```

`r htmltools::h2(tippy("Install", "It's on CRAN!"))`

Stable `r tippy("CRAN", "It's stable!")` release.

```{r, eval = FALSE}
install.packages("tippy") 
```

Or the `r tippy("development", "It's unstable!")` version.

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("JohnCoene/tippy")
remotes::install_bitbucket("JohnCoene/tippy")
```

`r htmltools::h2(tippy("Examples", "Examples!"))`

### R Markdown

In `r tippy("R markdown", "Just like this one!")`.

```{r}
library(tippy)

# standard
tippy("Hover me!", tooltip = "Hi, I'm the tooltip!")

tippy(
  "Hover me!", 
  tooltip = "Hi, I'm the tooltip!", 
  placement = "right",
  arrow = TRUE
)

tippy("<strong>Works with html!</strong>", 
  tooltip = "<strong>Hi</strong>, I'm the tooltip!", 
  allowHTML = TRUE,
  animation = "scale",
  duration = 1000, 
  placement = "bottom",
  theme = "light"
)

tippy(
  "Click me!", 
  tooltip = "Hi, I'm the tooltip!", 
  trigger = "click"
)
```

You can also use in `r tippy("in-line", "like this!")`, `tippy("like this", "Here's the tooltip")`.

### Shiny

Works in Shiny apps, you can apply the tooltip to another element with `with_tippy`.

```{r, eval = FALSE}
library(shiny)
library(tippy)

shinyApp(
  ui = fluidPage(
    
    with_tippy(
      textInput('text', 'Text'),
      tooltip = "TEXT"
    ),
    
    with_tippy(
      selectInput('select', 'Select', c('a', 'b')),
      "SELECT"
    ),
    
    with_tippy(
      numericInput('numeric', 'Numeric', NULL),
      "NUMERIC"
    ),
    
    with_tippy(
      radioButtons('radio', 'Radio', c('a', 'b')),
      "RADIO"
    ),
    
    with_tippy(
      checkboxInput('check', 'Check'),
      "CHECKBOX"
    ),
    
    with_tippy(
      actionButton('action', 'Action'),
      "BUTTON"
    ),
    
    with_tippy(
      sliderInput('slider', 'Slider', 0, 1, 0.5),
      "SLIDER"
    ),
    
    with_tippy(
      dateInput('date', 'Date'),
      "DATE"
    )
    
  ),
  server = function(input, output) {}
)
```

You can also `r tippy("easily", "just one function!")` call tippy on `r tippy("multiple elements", "As many as you want!")` at once with `tippy_class`

```{r, eval=FALSE}
library(shiny)

shinyApp(
  ui = fluidPage(
    fluidRow(
      column(
        3,
        h3("Same tooltip"),
        p("Some text", class = "tip"),
        p("Some text", class = "tip"),
        p("Some text", class = "tip"),
        p("Some text", class = "tip"),
        p("Some text", class = "tip"),
        p("Some text", class = "tip"),
        tippy_class("tip", content = "Tooltip")
      ),
      column(
        3, 
        h3("Different tooltips"),
        p("Some text", class = "tip2", `data-tippy-content` = "Tooltip 1"),
        p("Some text", class = "tip2", `data-tippy-content` = "Tooltip 2"),
        p("Some text", class = "tip2", `data-tippy-content` = "Tooltip 3"),
        tippy_class("tip2")
      )
    )
 ),
 server = function(input, output, session) {}
)
```

You __must__ pass `session` to your server function for it to work!