[![Build Status](https://travis-ci.org/JohnCoene/tippy.svg?branch=master)](https://travis-ci.org/JohnCoene/tippy) [![CRAN status](https://www.r-pkg.org/badges/version/tippy)](https://cran.r-project.org/package=tippy)

```{r, include=FALSE}
library(tippy)
library(htmltools)
```

```{r, echo=FALSE}
div(
  class = "row",
  div(
    class = "col-md-3",
    img(
      src = "logo.png",
      class = "responsive-img img-responsive"
    )
  ),
  div(
    class = "col-md-9",
    h1(
      tippy(
        "Tippy",
        "Tooltips!!!",
        size = "large"
      )
    ),
    br(),
    p(
      "A",
      tippy(
        "small package",
        "Just 6 functions!"
      ),
      "to include tooltips in Shiny apps and",
      tippy(
        "R Markdown documents",
        "Just like this one"
      )
    )
  )
)
```

`r htmltools::h2(tippy("Install", "It's on CRAN!"))`

Stable `r tippy("CRAN", "It's stable!")` release.

```{r, eval = FALSE}
install.packages("tippy") 
```

Or the `r tippy("development", "It's unstable!")` version.

```{r, eval = FALSE}
devtools::install_github("JohnCoene/tippy")
devtools::install_bitbucket("JohnCoene/tippy")
```

`r htmltools::h2(tippy("Examples", "Examples!"))`

### R Markdown

In `r tippy("R markdown", "Just like this one!")`.

```{r}
library(tippy)

# standard
tippy("Hover me!", tooltip = "Hi, I'm the tooltip!")

tippy(
  "Hover me!", 
  tooltip = "Hi, I'm the tooltip!", 
  placement = "right",
  arrow = TRUE
)

tippy("<strong>Works with html!</strong>", 
  tooltip = "Hi, I'm the tooltip!", 
  animation = "scale",
  duration = 1000, 
  placement = "bottom"
)

tippy(
  "Click me!", 
  tooltip = "Hi, I'm the tooltip!", 
  trigger = "click"
)
```

You can also use in in-line, `tippy("like this", "Here's the tooltip")`.

### Shiny

Works in Shiny apps.

```{r, eval = FALSE}
library(shiny)

ui <- fluidPage(
  br(), br(), br(),
  fluidRow(column(12, tippy("Standard tooltip", tooltip = "The tooltip"))),
  fluidRow(column(12, textInput("textInput", "text"))),
  tippy_this(element = "textInput", tooltip =  "Tooltip on other element")
)

server <- function(input, output){}

shinyApp(ui, server)
```

You can also easily call tippy on multiple elements at once.

```{r, eval=FALSE}
library(shiny)

shinyApp(
  ui = fluidPage(
    use_tippy(),
    p("Some text", title = "tooltip"),
    p("Some text", title = "tooltip"),
    p("Some text", title = "tooltip"),
    p("Some text", title = "tooltip"),
    p("Some text", title = "tooltip"),
    p("Some text", title = "tooltip"),
    call_tippy("[title]") # all elements with title
 ),
 server = function(input, output) {}
)
```
